Online {\IterComp}

### 2017-11-16 related.tex
related work

Older works attempted to drive \itercomp with execution time information~\cite{fursin:hal-01257279,fursin:inria-00001054}. They create
multiple versions of the hottest procedures, optimized and unoptimized, and at runtime randomly and dynamically select which one to use.
For each invocation, they record the time spent in the procedure and the version used. By comparing the average time required for each
invocation, they are able to evaluate the relative performance of different optimizations. The limitations of this approach are that it
depends on the amount of work performed by the procedure not changing dramatically from invocation to invocation and the number of
invocations being sufficiently high to collect multiple data points for each version. These drawbacks keep it from being a general solution
to the problem of iterative compilation.

>>>>

Some approaches attempt to drive \itercomp with execution time information~\cite{fursin:hal-01257279,fursin:inria-00001054,tiwari2011online}. They create
multiple versions of the hottest procedures, optimized and unoptimized, and they evaluate them at runtime on different invocations.
For each invocation, they record the time spent in the procedure and the version used. By comparing the average time required for each
invocation, they are able to evaluate the relative performance of different optimizations. The limitations of such approaches are that they
depend on the amount of work performed by the procedure not changing dramatically from invocation to invocation and the number of
invocations being sufficiently high to collect multiple data points for each version. These drawbacks keep it from being a general solution
to the problem of iterative compilation.
